Observed vs. Simulated Year Comparison

### 2023-05-11 03-post-process/compare-sim-to-obs.Rmd
Fix small file path bug introduced by recent changes
Very minor: I changed the output file to be called "output_scenario.rds" instead of "output-scenario.rds" in a commit as part of #185
Remove time-varying prespawn mort from sim-vs-obs

  # reorder rows
  x$Class = factor(x$Class, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
  x$Type = factor(x$Type, levels = c("Egg to Parr Survival", "Parr Mean Size", "Proportion Fall Migrants", "Overwinter Survival", "Parr to Smolt Mean Size 'Growth Factor'", "Smolt Mean Size", "Migration to LGR Survival", "LGR to Ocean Survival", "First Year Ocean Survival", "Age-3 Maturity", "Age-4 Maturity", "BON to LGR Survival", "Pre-Spawn Survival"))
  x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
  x$origin = factor(x$origin, levels = c("NOR", "HOR", "Combined"))
  x = x[order(x$Class, x$Type, x$LH_type, x$origin),]

@@

#### Pre-Spawn Survival

```{r}
x = lapply(1:4, function(j) get_ratio("^phi_Sb_Sa[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Pre-Spawn Survival: Estimates")
ratio_plots(x, "Pre-Spawn Survival: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Adult", Type = "Pre-Spawn Survival"))
```

@@

#### Pre-Spawn Survival

```{r}
pop_ts_plots("^phi_Sb_Sa[year,pop]")
```

>>>>

  # reorder rows
  x$Class = factor(x$Class, levels = c("FW Juvenile", "SW Juvenile", "FW Adult"))
  x$Type = factor(x$Type, levels = c("Egg to Parr Survival", "Parr Mean Size", "Proportion Fall Migrants", "Overwinter Survival", "Parr to Smolt Mean Size 'Growth Factor'", "Smolt Mean Size", "Migration to LGR Survival", "LGR to Ocean Survival", "First Year Ocean Survival", "Age-3 Maturity", "Age-4 Maturity", "BON to LGR Survival"))
  x$LH_type = factor(x$LH_type, levels = c("Combined", "Fall", "Spring"))
  x$origin = factor(x$origin, levels = c("NOR", "HOR", "Combined"))
  x = x[order(x$Class, x$Type, x$LH_type, x$origin),]

@@

@@
